SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-12-08 toplas26/intro.tex
typo fix

The current work extends previous work \cite{skalka-near-esop25} as
discussed above. Key differences as noted in Figure
\ref{fig-comp-wrap} include a Hoare logic and a more expressive
confidentiality type systems supporting analysis of more complex
programs that enforces passive security in the real/ideal model, vs.~a
weaker gradual release property as in \cite{skalka-near-esop25}.
Furthermore our Hoare logic analysis has been fully implemented in the
current work in an Antlr/Scala/cvc5-based framework.

>>>>

The current work extends previous work \cite{skalka-near-esop25} as
discussed above. Key differences as noted in Figure
\ref{fig-comp-wrap} include a Hoare logic and a more expressive
confidentiality type system supporting analysis of more complex
programs that enforces passive security in the real/ideal model, vs.~a
weaker gradual release property as in \cite{skalka-near-esop25}.
Furthermore our Hoare logic analysis has been fully implemented in the
current work in an Antlr/Scala/cvc5-based framework.
